BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-15 tex/1-intro.tex
test
Started on the new intro

>>>>

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value. In contrast to books, newspapers or centralized web platforms like FaceBook and Twitter, there is no standard method or authority that ensures blog archiving and long-term digital preservation. \TODO{Somewere, \cite{anderson2012}}.

Yet, blogs are an important part of today's web

By June 2008 the Technorati Internet search engine for blogs reported indexing 112.8 million blogs \cite{technoratidata2008}

Given the nature of blogs, they are expectedly highly volatile web resources.

Recently, they have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012},

Blogs are a popular means of communication and expression of ideas and have been adopted by universities, institutions and scolars (reference?). Recently, blogs have also been used to disseminate ideas in times of political turmoil or even war\cite{nahedeltantawy2012}. Their political, scientific and cultural significance is undisputed. (rephrase to avoid need for reference?)
